---
title: "fars"
author: "Philip Gregory"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Package Description 

The `fars` package reads data from Fatality Analysis Reporting System (FARS)  
from the [National Highway Traffic Safety 
Administration](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars).

[FARS](https://en.wikipedia.org/wiki/Fatality_Analysis_Reporting_System) is a
nationwide census, providing the American public yearly data, regarding fatal
injuries suffered in motor vehicle traffic crashes.

The package plots accidents on a map plot by year and state


## Load Packages

```{r}
library(fars)
library(maps)
```


## Included data

Data files included within the package are:

```{r}
list.files(system.file("extdata", package = "fars"))
```


## Package Functions

### Function `fars_read`

This function loads data from a comma separated file taken from the  US
National Highway Traffic Safetyc Administration's Fatality Analysis
Reporting System (FARS).

```{r}
#fars_read(filename)
```


### Function `make_filename`

This function requires a year as input and returns a full FARS filename.

```{r}
yr <- 2015
make_filename(yr)
```

### Function `fars_read_years`

This function used by `fars_summarize_years`

```{r}
fars_read_years(2013)
```


### Function `fars_summarize_years`

This function summarises yearly accidents data, by month.

```{r}
#plot(fars_summarize_years(2015))
#fars_summarize_years(c(2015, 2014))
```

### Function `fars_map_state`

The function displays a state map plot including accidents location
by year

```{r}
#state_num <- 49 # Utah
#yr <- 2014
#fars_map_state(state_num, yr)
```


